Multi-modality Imagery Database for Plant Phenotyping

### 2015-07-22 datapaper_hardware.tex
Merge

\subsubsection{Fluorescence and IR Images}
Chlorophyll {\it a} fluorescence images were captured once every hour during the daylight period in a growth chamber~\cite{cruz2015depi}.
A set of $5$ images were captured using a Hitachi KP-F145GV CCD camera (Hitachi Kokusai Electric America Inc., Woodbury, NY) outfitted with an infrared long pass filter (Schott Glass RG-9, Thorlabs, Newton, NJ), during a short period ($<400~ms$) of intense light saturating to photosynthesis ($>10,000~\mu mol~photons~m^{-2} s^{-1}$) provided by an array of white Cree LEDs (XMLAWT, 5700K color temperature, Digi-Key, Thief River Falls, MN) collimated using a $20~mm$ Carclo Lens (10003, LED Supply, Lakewood, CO).
%
Chlorophyll {\it a} fluorescence was excited using monochromatic red LEDs (Everlight $625~nm$, ELSH-F51R1-0LPNM-AR5R6, Digi-Key), collimated using a Ledil reflector optic ($C11347\_REGINA$, Mouser Electronics, Mansfield, TX) and pulsed for $50~\mu s$ during a brief window when the white LEDs were electronically shuttered.
In addition, a series of $5$ images were also collected in the absence of the excitation light for artifact subtraction.

Infrared images were collected once every hour with the same camera and filter used for chlorophyll {\it a} fluorescence.
Pulses of $940nm$ light were provided by an array of OSRAM LEDs (SFH 4239, Digi-Key), collimated using a Polymer Optics lens (Part no. 170, Polymer Optics Ltd., Berkshire, England).
Since $940nm$ light does not influence plant development or drive photosynthesis, images were also collected during the night period~\cite{eskins1992light}.
%
Precisely, phytochromes are the closest photoreceptors that absorb in the far red, near infrared region, but the action spectrum is diminished to zero or near zero ($>800nm$) in the region where we do IR reflectance ($940nm$)~\cite{butler1964actton}.
%
Note that the other modalities were captured only at day time, so that they will not interfere plant growth.

@@

The RGB color and depth images were collected using a Creative Senz3D sensor~\cite{nguyen2015vietnamese}. The sensor contains both a $1280 \times 720$ color camera directed parallel to, and separated by roughly $25~mm$ from, a depth camera which has a resolution of $320\times240$ pixels.
The depth sensor uses a flash near IR illuminator and measures the time-of-flight~\cite{Hansard2013} of the beam at each pixel to obtain depth estimates along with an IR reflectance at each pixel.

There are a number of limitations to the depth sensor that become the sources of depth errors.
The primary measurement limitation on the range-to-target is the strength of the reflected beam.
As a result, dark, matt surfaces are measured reliably only at a close range on the order of $20$ or $30~cm$.
Highly reflective surfaces also pose problems with direct reflections leading to saturation and highly unreliable depths.
In addition reflective surfaces at grazing angles are less reliably measured since little signal is reflected.
Fortunately the primary goal of the depth measurements are to obtain leaf depths, and plants provide good, roughly Lambertian, reflections of IR~\cite{Chelle2006219}.  Thus the depth pixels that are most reliable and are of most use are those that fall on plant foliage.

@@

\subsubsection{Image collection}
The imagery data, including the fluorescent image, the IR reflectance image,  the color image, and the $3$D depth image, were collected once every hour.
%
Five minutes before the end of each hour, $3$D depth images and the color image were captured using the Creative Senz3D sensor (the depth points were transformed into the world coordinates and expressed in the unit of $mm$), followed by fluorescence and the IR reflectance images collected sequentially at 2 minute intervals by the IR filtered CCD camera.
%
No substantial movements or growth were observed within the about four minute period required for image capture using all four modalities, minimizing potential problems in image calibration.

>>>>

\subsubsection{Fluorescence and IR Images}
Chlorophyll {\it a} fluorescence images were captured once every hour during the daylight period in a growth chamber~\cite{cruz2015depi}.
A set of $5$ images were captured using a Hitachi KP-F145GV CCD camera (Hitachi Kokusai Electric America Inc., Woodbury, NY) outfitted with an infrared long pass filter (Schott Glass RG-$9$, Thorlabs, Newton, NJ), during a short period ($<400~ms$) of intense light saturating to photosynthesis ($>10,000~\mu mol~photons~m^{-2} s^{-1}$) provided by an array of white Cree LEDs (XMLAWT, $5700$K color temperature, Digi-Key, Thief River Falls, MN) collimated using a $20~mm$ Carclo Lens ($10003$, LED Supply, Lakewood, CO).
%
Chlorophyll {\it a} fluorescence was excited using monochromatic red LEDs (Everlight $625~nm$, ELSH-F51R1-0LPNM-AR5R6, Digi-Key), collimated using a Ledil reflector optic ($C11347\_REGINA$, Mouser Electronics, Mansfield, TX) and pulsed for $50~\mu s$ during a brief window when the white LEDs were electronically shuttered.
In addition, a series of $5$ images were also collected in the absence of the excitation light for artifact subtraction.

Infrared images were collected once every hour with the same camera and filter used for chlorophyll {\it a} fluorescence.
Pulses of $940nm$ light were provided by an array of OSRAM LEDs (SFH $4239$, Digi-Key), collimated using a Polymer Optics lens (Part no. $170$, Polymer Optics Ltd., Berkshire, England).
Since $940nm$ light does not influence plant development or drive photosynthesis, images were also collected during the night period~\cite{eskins1992light}.
%
Precisely, phytochromes are the closest photoreceptors that absorb in the far red, near infrared region, but the action spectrum is diminished to zero or near zero ($>800nm$) in the region where we do IR reflectance ($940nm$)~\cite{butler1964actton}.
%
Note that the other modalities were captured only at day time, so that they will not interfere plant growth.

@@

The RGB color and depth images were collected using a Creative Senz3D sensor~\cite{nguyen2015vietnamese}. 
The sensor contains both a $1,280 \times 720$ color camera directed parallel to, and separated by roughly $25mm$ from, a depth camera which has a resolution of $320\times240$ pixels.
The depth sensor uses a flash near IR illuminator and measures the time-of-flight~\cite{Hansard2013} of the beam at each pixel to obtain depth estimates along with an IR reflectance at each pixel.

There is a number of limitations to the depth sensor that becomes the sources of depth errors.
The primary measurement limitation on the range-to-target is the strength of the reflected beam.
As a result, dark, matt surfaces are measured reliably only at a close range on the order of $20$ or $30cm$.
Highly reflective surfaces also pose problems with direct reflections leading to saturation and highly unreliable depths.
In addition reflective surfaces at grazing angles are less reliably measured since little signal is reflected.
Fortunately the primary goal of the depth measurements are to obtain leaf depths, and plants provide good, roughly Lambertian, reflections of IR~\cite{Chelle2006219}.  
Thus the depth pixels that are most reliable and are of most use are those that fall on plant foliage.

@@

\subsubsection{Image collection}
The imagery data, including fluorescence, IR reflectance,  RGB color, and the $3$D depth images, is collected once every hour.
%
Five minutes before the end of each hour, $3$D depth images and the color image were captured using the Creative Senz3D sensor (the depth points were transformed into the world coordinates and expressed in the unit of $mm$), followed by fluorescence and IR reflectance images collected sequentially at $2$-minute interval by the IR filtered CCD camera.
%
No substantial movements or growth were observed within the about four-minute period required for image capture using all four modalities, minimizing potential problems in image calibration.
